%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Mobile Engineer Intern} % Job title
  {LinkedIn} % Organization
  {Sunnyvale, CA} % Location
  {Jun. 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented upsells for new features on LinkedIn’s iOS application in \textbf{Swift} and \textbf{Objective-C} towards driving increased Premium subscriptions. }
      \item {Utilized \textbf{GraphQL} to build reusable \textbf{UIKit} components from API-driven content, maximizing code reuse and minimizing technical debt.}
      \item {Wrote unit, layout, and scenario tests utilizing the XCTest framework in order to minimize regressions and reduce debugging time.}
    \end{cvitems}
  }


%---------------------------------------------------------
\cventry
  {Software Engineer Intern} % Job title
  {MaXentric} % Organization
  {San Diego, CA} % Location
  {Jun. 2022 - Sep. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and built cross-platform web, iOS, and Android app using \textbf{Ionic} and \textbf{Capacitor} frameworks in \textbf{Vue.js} with \textbf{TypeScript} to interface with medical device over Bluetooth LE and graph heart rate data in real time.}
      \item {Implemented frame check sequence in \textbf{C} for Wi‐fi MAC layer towards building 5G communication platform on a Xilinx FPGA.}
    \end{cvitems}
  }


%---------------------------------------------------------
\cventry
  {Instructional Assistant} % Job title
  {UCSD Computer Science and Engineering Department} % Organization
  {San Diego, CA} % Location
  {Aug. 2021 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Taught \textbf{500+} undergraduate students \textbf{C}, \textbf{C++}, and \textbf{ARM} assembly for systems programming and data structures courses.}
      \item {Hosted guided lab hours and one-on-one sessions to assist students with pointers and memory management, basic processor circuits, \textbf{Linux CLI}, and data structures.}
    \end{cvitems}
  }


%---------------------------------------------------------
\cventry
  {Software Engineer Intern} % Job title
  {Social Chat} % Organization
  {San Francisco, CA} % Location
  {Jul. 2021 - Sep. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Redesigned homepage for livestreamed video shopping platform in \textbf{JavaScript}, \textbf{HTML}, and \textbf{CSS} to optimize conversion rate and improve usability.}
      \item {Employed \textbf{Django} and custom \textbf{Bootstrap} templates to automatically populate and update webpage information from back-end \textbf{PostgreSQL} database, eliminating the need for manual data entry and styling.}
    \end{cvitems}
  }



%---------------------------------------------------------
\end{cventries}
